Motional Ground-State Cooling Outside the Lamb-Dicke Regime -- Supplemental material

### 2018-04-17 sm.tex
Zoomed in plots

>>>>

\section{Zooming into the cooling sidebands}
The height of the cooling sidebands decreases to about $2\%$ after the Raman sideband cooling,
making them very hard to see on when plotting on the same scale as the heating sideband
as well as the spectra before cooling. A zoom-in of the spectra after cooling
is included here so that they can be seen more clearly.
Only the cooling orders ($\Delta n=-1,-2$ for radial X and Y axes and $\Delta n=-1, \dots, -5$ for axial Z axis) are shown.

\includegraphics[height=4cm]{spectrum_zoom_cool_rx.pdf}
\includegraphics[height=4cm]{spectrum_zoom_cool_ry.pdf}
\includegraphics[height=4cm]{spectrum_zoom_cool_az.pdf}
